---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sufficientForecasting

<!-- badges: start -->

<!-- badges: end -->

## Overview

The goal of sufficientForecasting is to forecast a single time series when there is a large number of predictors and a possible nonlinear effect.

## Installation

You can install the development version of sufficientForecasting like so:

``` r
# The easiest way to install sufficientForecasting
install.packages("sufficientForecasting")
# OR
devtools::install_github("JingFu1224/sufficientForecasting")
```

## Usage

The following example uses SF.CI to solve a problem: forecast a single time series, 
and its upper bound and lower bound

```{r example}
library(sufficientForecasting)
## basic example code
SF.CI(y=dataExample$y,X=dataExample$X,newX=dataExample$newX,type="LLM",alpha = 0.05)
```


